Software Defect Prediction: Review, Commentary, and Future Work

### 2015-12-14 paper/paper.tex
start on abstract

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings. It is an {\em alternate} style which produces
a {\em tighter-looking} paper and was designed in response to
concerns expressed, by authors, over page-budgets.
It complements the document \textit{Author's (Alternate) Guide to
Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
This source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file. A compiled PDF version
is available on the web page to help you with the
`look and feel'.
\end{abstract}

@@

\keywords{Fault prediction model; Software mining; Ant Colony Optimization; Classification}

>>>>

\maketitle
\begin{abstract}
This paper provides a comprehensive review and commentary on software defect prediction research. Review and criticism of previous work is presented. Future steps in the domain are given.
\end{abstract}

@@

\keywords{Fault prediction model, Software mining, Ant Colony Optimization, Classification, Defect Prediction}
